---
title: "A Python Package for Density Ratio Estimation"
author: Koji MAKIYAMA (@hoxo_m)
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE
)
```

## 1. Overview

**Density ratio estimation** is described as follows: for given two data samples `x` and `y` from unknown distributions `p(x)` and `q(y)` respectively, estimate `w(x) = p(x) / q(x)`, where `x` and `y` are d-dimensional real numbers.

The estimated density ratio function `w(x)` can be used in many applications such as the inlier-based outlier detection [1] and covariate shift adaptation [2].
Other useful applications about density ratio estimation were summarized by Sugiyama et al. (2012) [3].

The package **densratio** provides a function `densratio()` that returns a result has the function to estimate density ratio `compute_density_ratio()`.

For example, 
a
```{r engine="python", eval=FALSE}
from scipy.stats import norm
from densratio import densratio

x = norm.rvs(size = 200, loc = 1, scale = 1./8, random_state = 71)
y = norm.rvs(size = 200, loc = 1, scale = 1./2, random_state = 71)
result = densratio(x, y)
print(result)
```

```{r engine="python", echo=FALSE}
from scipy.stats import norm
from densratio import densratio

x = norm.rvs(size = 200, loc = 0, scale = 1./8, random_state = 71)
y = norm.rvs(size = 200, loc = 0, scale = 1./2, random_state = 71)
result = densratio(x, y, verbose = False)
print(result)
```


## 2. How to Install

You can install the package from GitHub.

```:sh
$ pip install git+https://github.com/hoxo-m/densratio_py.git
```

